The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-07-31 paper/iphas-dr2-rev1.tex
-

\begin{figure}
    \includegraphics[width=\linewidth]{figures/spitzer-ccd/spitzer-ccd.pdf} 
    \caption{Spitzer/GLIMPSE colour-colour diagram towards Sh~2-82,
    showing the objects for which a counterpart exists in IPHAS
    (845 objects, grey circles) 
    and those for which no counterpart was identified 
    (511 objects, red crosses).
    A cross-matching radius of 1 arcsec
    was used to identify counterparts.
    The arrow illustrates the reddening vector corresponding
    to $A_{Ks}=3$ following the reddening law due to \citet{Flaherty2007}.
    It is apparent that the most heavily reddened objects
    tend to have no counterpart.
    Three heavily-reddened objects without counterpart
    are located above the diagram but are not shown for clarity. }
    \label{fig:spitzer-ccd}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{figures/spitzer-ccd/spitzer-ccd.pdf} 
    \caption{Spitzer/GLIMPSE colour-colour diagram towards Sh~2-82,
    showing the objects for which a counterpart exists in IPHAS
    (845 objects, grey circles) 
    and those for which no counterpart was identified 
    (511 objects, red crosses).
    A cross-matching radius of 1 arcsec
    was used to identify counterparts.
    The arrow illustrates the reddening vector corresponding
    to $A_{Ks}=3$ following the reddening law due to \citet{Flaherty2007}.
    It is apparent that objects near the top of the diagram,
    where heavily reddened objects are expected to sit,
    tend to have no counterpart.
    In contrast, many of the objects on the right hand side of the diagram,
    where YSOs are expected to sit, do have counterparts.
    %We note that three heavily-reddened objects without counterpart
    %are located above the diagram but are not shown for clarity. 
    }
    \label{fig:spitzer-ccd}
\end{figure}
